3.8: Polynomial Regression

### 2019-11-20 static/slides/20-slides.Rmd
Last tweak to slides 20
Add R practice 19 answers

- **Linear**: 
  - slope $(\hat{\beta_1})$, $\frac{\Delta X}{\Delta Y}$ same for all $X$

@@

- **Polynomial**:
  - slope $(\hat{\beta_1})$, $\frac{\Delta X}{\Delta Y}$ *depends on the value of* $X$

@@

- **Interaction Effect**:
  - slope $(\hat{\beta_1})$, $\frac{\Delta X_1}{\Delta Y}$ *depends on the value of* $X_2$

@@

```{}
tidy(reg1)
```
]
--

>>>>

- **Linear**: 
  - slope $(\hat{\beta_1})$, $\frac{\Delta Y}{\Delta X}$ same for all $X$

@@

- **Polynomial**:
  - slope $(\hat{\beta_1})$, $\frac{\Delta Y}{\Delta X}$ *depends on the value of* $X$

@@

- **Interaction Effect**:
  - slope $(\hat{\beta_1})$, $\frac{\Delta Y}{\Delta X_1}$ *depends on the value of* $X_2$

@@

```{r}
tidy(reg1)
```
]
